### 2022-01-17 reviews/rebuttal.tex

\vspace{0.5cm}

\end{reply}

\begin{point}
What if the true generator process is a mixture model, in such a way that there is not a unique solution to the minimal subset variable selection problem? In fact, how can you assure that the minimal subset variable selection problems have only one selection? I think that the algorithm described in appendix A should take into account this possibility, and the step 5 not to choose the smallest (model) that is sufficient close to the reference model's predictive utility score but to use, for instance, an Occam window, that reflects more adequately the uncertainty associated with the model selection process something that, apparently, your methodology does not consider. In fact, and even though in your examples your results in the paper were not sensitive to the specific choice of how “sufficiently close” is defined, I guess that there can be situations where this statement is not true, and more of one solution to the minimal subset variable selection problem and to the complete variable selection problem could exist.
\end{point}

\begin{reply}
The projection predictive variable selection and its properties have been extensively discussed in \citet{piironen2017comparison} and \citet{piironen2020projective}, and we refer to them for the detailed discussion on the uncertainty related to search paths. \citet{paasiniemi2018} provides illustrations how this uncertainty can be communicated to the users. When there are correlating variables that have exactly the same amount of information, the minimal set is not unique. In this paper, we focused on the average performance of the minimal set, but when analysing a single dataset, we recommend the approaches presented in \citet{paasiniemi2018} to analyse alternative possible variable sets.

\fede{We clarified this point in the paper in Section 3, writing:}

\textit{``Such nature of the minimal subset makes the solution
	not unique, except in the particular case of completely orthogonal predictors. 
	The non-uniqueness of the solution is not a problem per se, as different samples of the data
	are expected to give possible different minimal subsets but with same predictive power. 
	However, it makes it difficult to define a proper
	concept of stability of the selection.''}
\end{reply}

@@

\begin{point}
It is not very exigent in (2) to impose that $\text{elpd}_i-\text{elpd}_\text{best}>0$? Perhaps you should consider other limits similar to those used in Bayes factors (Kass and Raftery, 1995) and not to choose only on solution but to explore other possible solutions in the spirit of Occam’s window
\end{point}

\begin{reply}
The above condition is derived from the original criteria to choose the model size in \citet{piironen2020projective} for the use of the projection predictive approach in the minimal subset scenario. In that case, the comparison is between the predictive score of the submodel of size $i$ and the reference model. Here we decided to compare the submodel of size $i$ with the ``best'' size, at the given iteration, due to the natural loss of explanatory power of the remaining covariates as the iterations increase. \\
In general, the condition is expressed as the probability of that event, which is anyhow less exigent than the inequality itself. We don't want to imply that this procedure could not be improved somehow to take, for example, something like Occam's window into account. However, since this was not the main aim of this paper, we cannot reasonably address it here but will leave it for future research.
TODO: is it worth adding a small sentence in the manuscropt about this?
\end{reply}

\begin{point}
Section 4.1: It is no clear how the value of $\alpha$ should be chosen. $\alpha= 0.16$ is a magic number and a more thoroughly discussion of the influence of this value should be provided.
\end{point}

\begin{reply}
TODO: clarify this in the paper
\fede{We clarified the choice of $\alpha$ by writing in Section 4.1:}

\textit{``The choice of $\alpha$ to determine the submodel size is discussed in \citet{piironen2020projective}. One possible way to proceed, but just as rule of thumb, is to choose $\alpha=0.16$, which correspond to requiring that the submodel predictive score is at most at one standard deviation distance from the best submodel predictive score.''}
